State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-22 paper/chapters/4_classification.tex
paper: add description of naive bayes

@@

@@

\subsubsection*{Maimum Entropy}

>>>>

This technique is based on a simple stochastic model that for a given document $d$ tries to find the most likely class $c^* = \mathrm{arg max}_c P(c \vert d)$ where $c$ stands for one out of a number of possible classes and $P(c \vert d)$ denotes the conditional probability that document $d$ can be assigned to $c$. For example, in sentiment analysis $c^*$ would denote the sentiment value that could be assigned to document $d$. $c^*$ is computed by applying Bayes' rule,

@@

for each possible sentiment value $c$. $P(d \vert c)$ has to be estimated and therefore it is presumed that there exists a predefined set of features $\lbrace f_1, \ldots , f_m \rbrace$ which are assumed to be conditionally independent. Based on this estimation the actual rule that can be used for classification is derived from Bayes' rule:

@@

Here, $n_i(d)$ designates the number of occurrences of feature $f_i$ in document $d$.

\subsubsection*{Maximum Entropy}
